\footnotesize{
\begin{longtable}[H]{  | >{\bfseries}l | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{4cm} | } \hline

    Name
    & \multicolumn{4}{l |}{AnalysisViewController} \\ \hline

    Description
    & \multicolumn{4}{p{8.5cm} |}{
    The AnalysisViewController manages the analysis view and provides the functions that let the user confirm the border calculation and edit metadata associated with a captured image.

    } \\ \hline

    Type
    & \multicolumn{4}{l |}{Class}
    \\ \hline

    Implemented In
    & \multicolumn{4}{l |}{controllers/camera.js}
    \\ \hline

    Attributes
    & Name & Type & \multicolumn{2}{l |}{Description} \\ \hline

        & MDAppState & class & \multicolumn{2}{p{5.5cm} |}{
        When a new image is captured, the CameraViewController notifies the MDAppState that a new image is the active image.
        } \\ \hline

        & MDLesionImage & class & \multicolumn{2}{p{5.5cm} |}{
        When a new image is captured the CameraViewController notifies the MDLesionImage class which creates a new MDLesionImage instance.
        } \\ \hline

        & MDMetadata & class & \multicolumn{2}{p{5.5cm} |}{
        When a new image is captured the CameraViewController notifies the MDLesionImage class which creates a new MDLesionImage instance.
        } \\ \hline

        & activeImage & instance of MDLesionImage & \multicolumn{2}{p{5.5cm} |}{
        When a new image is captured the CameraViewController notifies the MDLesionImage class which creates a new MDLesionImage instance.
        } \\ \hline

        & activeMetadata & instance of MDMetadata & \multicolumn{2}{p{5.5cm} |}{
        When a new image is captured the CameraViewController notifies the MDLesionImage class which creates a new MDLesionImage instance.
        } \\ \hline


    Methods
    & Name & Parameter & Return Type & Description \\ \hline

        & confirmBorder & confirm : boolean & void
        & This method is triggered by the user and passed from the view to the view controller. The event is passed on to the MDCameraService along with a reference to the captureImageCallback which is called when an image has been saved.
        \\ \hline
        & tdsAnalysisCallback & results & void
        & The MDCameraService notifies the CameraViewController that an image is availble via this callback. The results parameter is a javascript object that contains a path to the captured image file and a preview image file.
        \\ \hline
        & saveData & void & void
        & When the camera view is loaded this method is called by the angular ui-router. The CameraViewController maked selected background UI components transparent in order to allow the camera preivew view to become visible.
        \\ \hline


    \caption{AnalysisViewController Specification}
    \label{fig:analysis_controller}
\end{longtable}
}