\setlength{\tabcolsep}{0.5em}
\footnotesize{
\begin{longtable}[H]{  | >{\bfseries}p{2cm} | p{2.2cm} | p{1.5cm} | p{1.5cm} | p{4cm} | } \hline

    Name
    & \multicolumn{4}{l |}{ArchiveDetailViewController} \\ \hline

    Description
    & \multicolumn{4}{p{9.5cm} |}{
    Controller for the archive detail view. The id of the selected LesionImage is passed to this controller when loaded. The controller prepares the data of the selected archived image to be presented to the use in the archive detail view. This controllers methods are responsible for saving edited metadata back to the archive or sending images and data via email.
    } \\ \hline

    Type
    & \multicolumn{4}{l |}{Class}
    \\ \hline

    Implemented In
    & \multicolumn{4}{l |}{services/data.js}
    \\ \hline

    Attributes
    & Name & Type & \multicolumn{2}{l |}{Description} \\ \hline

        & MDLesionImage & class & \multicolumn{2}{p{5.5cm} |}{
        MDLesionImage provides the controller with an instance of an MDLesionImage.
        } \\ \hline

        & MDMetadata & class & \multicolumn{2}{p{5.5cm} |}{
        MDMetadata provides the controller with metadata associated with an instance of MDLesionImage
        } \\ \hline

        & activeImage & instance of MDLesionImage & \multicolumn{2}{p{5.5cm} |}{
        This is the selected instance of MDLesionImage to be presented to the user in the detail view.
        } \\ \hline

        & activeMetadata & instance of MDMetadata & \multicolumn{2}{p{5.5cm} |}{
        This is an instance of the metadata assciated with the selected MDLesionImage instance.
        } \\ \hline

    Methods
    & Name & Parameter & Return Type & Description \\ \hline

        & emailDetail & key & void
        & the data from the activeImage and activeMetadata is flattended to an html template and passed to the email service.
        \\ \hline

        & saveData & void & void
        & Any user edits to the metadata will be saved.
        \\ \hline

    \caption{ArchiveDetailViewController Specification}
    \label{fig:archivedetail_controller}
\end{longtable}
}