\setlength{\tabcolsep}{0.5em}
\footnotesize{
\begin{longtable}[H]{  | >{\bfseries}p{2cm} | p{2.2cm} | p{1.5cm} | p{1.5cm} | p{4cm} | } \hline

    Name
    & \multicolumn{4}{l |}{MDDataService} \\ \hline

    Description
    & \multicolumn{4}{p{9.5cm} |}{
    The MDDataService is a singelton class that encapsulates all the database access and management functions. MDDataService wraps two external services, the Cordova-sqlite-storage plugins and the persistence.js javascript library. The Cordova-sqlite-storage plugin manages connectivity to the sqlite database file. Persistence.js is an ORM library that hides away any messy sequel development behind a nice object oriented api.
    } \\ \hline

    Type
    & \multicolumn{4}{l |}{Class}
    \\ \hline

    Implemented In
    & \multicolumn{4}{l |}{services/data.js}
    \\ \hline

    Attributes
    & Name & Type & \multicolumn{2}{l |}{Description} \\ \hline

        & db & object & \multicolumn{2}{p{5.5cm} |}{
        The database object provided by the Cordova-sqlite-storage plugin.
        } \\ \hline



    Methods
    & Name & Parameter & Return Type & Description \\ \hline

        & initializeDB & void & void
        & This opens a connection to the sqlite database file and creates the table structure in the database if it does not already exist. This method must be called after the Cordova environment has loaded and the application context is ready.
        \\ \hline

        & saveData & void & void
        & This method saves any changes made to instantiated data objects.
        \\ \hline

    \caption{MDDataService Specification}
    \label{fig:data_service}
\end{longtable}
}